The Hydrogen Epoch of Reionization Array Dish: Characterization with Electromagnetic Simulations

### 2016-02-19 DishSimulations/paper/DishSimulationsPaper_v0.tex
Stuck in merge conflict  Please enter the commit message for your changes. Lines starting

\begin{equation}
\widetilde{v}_i(t) = \int d \Omega \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau') \widetilde{s}({\bf \widehat{k}},t+\tau_i - \tau)
\end{equation}

 An FX (or XF) correlator measures the time-averaged product of the fourier transform of the voltage streams between the $i^{th}$ and $j^{th}$ antenna. Fourier transforming the voltage stream from the $i^{th}$ antenna we obtain
\begin{equation}
v_i(f) = \int d \Omega \int d \tau' \widetilde{r}_i({\bf \widehat{k}},\tau') s({\bf \widehat{k}},f)e^{2 \pi i f(\tau'-\tau_i)}
\end{equation}
The time averaged product between the two antennas is
\begin{equation}
V_{ij}'(f) = \left \langle v_i(f) v_j^*(f) \right \rangle_t = \int d \Omega \int d \tau \widetilde{r}_i(\tau) d \tau' \widetilde{r}^*_j(\tau')e^{2 \pi i f (\tau'-\tau) } I({\bf \widehat{k}}, f) e^{- 2 \pi i \Delta \tau_{ij}f} 
\end{equation}
where $\Delta \tau_{ij} = \tau_i-\tau_j = ({\bf x_i - x_j}) \cdot {\bf \widehat{k}}/c$. We eliminated one of the solid angle integrals using equation~\ref{eq:Dirac}.

@@

Rather, we employ CST's time domain mode to simulate the response of the dish to plane waves incident off of zenith to understand the frequency dependence of the side-lobes using the same technique that was described in \S~\ref{ssec:Deconvolve}. In Fig.~\ref{fig:Comparison}, we show the delay structure of the sidelobe response functions we obtain on a N-S line $20^\circ$ and $30^\circ$ from zenith, which approximately correspond to the sidelobes of the beam.

\section{The Effect of the HERA dish Chromaticity on Foreground Leakage and Sensitivity}\label{sec:Foregrounds}

@@

>>>>

\begin{equation}
\widetilde{v}_i(t) = \int d \Omega \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau) \widetilde{s}({\bf \widehat{k}},t- \tau_i - \tau)
\end{equation}

 An FX (or XF) correlator measures the time-averaged product of the fourier transform of the voltage streams between the $i^{th}$ and $j^{th}$ antenna. Fourier transforming the voltage stream from the $i^{th}$ antenna we obtain
\begin{equation}
v_i(f) = \int d \Omega \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau) s({\bf \widehat{k}},f)e^{-2 \pi i f(\tau_i+\tau)}
\end{equation}
The time averaged product between the two antennas is
\begin{equation}
V_{ij}'(f) = \left \langle v_i(f) v_j^*(f) \right \rangle_t = \int d \Omega \int d \tau \widetilde{r}_i(\tau) d \tau' \widetilde{r}^*_j(\tau')e^{-2 \pi i f (\tau-\tau') } I({\bf \widehat{k}}, f) e^{- 2 \pi i \Delta \tau_{ij}f} 
\end{equation}
where $\Delta \tau_{ij} = \tau_i-\tau_j = ({\bf x_i - x_j}) \cdot {\bf \widehat{k}}/c$. We eliminated one of the solid angle integrals using equation~\ref{eq:Dirac}.

@@

Rather, we employ CST's time domain mode to simulate the response of the dish to plane waves incident off of zenith to understand the frequency dependence of the side-lobes using the same technique that was described in \S~\ref{ssec:Deconvolve}. In Fig.~\ref{fig:Sidelobes}, we show the delay structure of the sidelobe response functions we obtain on a N-S line $20^\circ$ and $30^\circ$ from zenith, which approximately corresponds to the first two nulls of the beam. Each response is normalized to the voltage response at zero delay and zenith. We see that at zero delay, the sidelobes are $\approx 20-25$\,dB down. However, at larger delays, $\approx 100$\,ns, the difference with the $20^\circ$ sidelobe is only $\approx 5-10$\,dB while the $30^\circ$ sidelobe maintains $\approx 15-20$\,dB separation with the zenith response. This behavior indicates that while the overall amplitude of the sidelobes is reduced at zero-delay, the enhanced frequency structure over the sidelobes can mitigate this advantage at high delays, leading for the brightness of sidelobe foregrounds, leaked at $\gtrsim 100$\,ns to appear just as bright as the leakage of foregrounds from zenith at $\gtrsim 100$\,ns.

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures/compareSidelobesNormalized.pdf}
\caption{The modulus square of the voltage responses of the HERA dish to plane waves incident from zenith (blue line) along with $20^\circ$,$25^\circ$, and $30^\circ$ off-zenith along the NS line. While the sidelobes are suppressed to $\approx 20-25$\,dB at zero delay, they come within $5$\,dB of the zenith response at longer delays which can lead to the level of leakage for a soruce in the sidelobes being comparable to the leakage of a source from zenith. The fact that the sidelobes occupy a much larger solid angle with only moderate supression at $\sim 100$\,ns coupled with their proximity to the horizon, suggests that they will dominate supra-horizon emission.}
\end{figure}

\section{The Effect of the HERA dish Chromaticity on Foreground Leakage and Sensitivity}
Having a thorough understanding of how the chromatic beam of the HERA dish leaks foregrounds into higher delays and a decent picture of the relevant voltage response of the dish itself, we are now in a position to explore the impact of the Dish's performance on the leakage of foregrounds beyond the wedge, and into the EoR window. Beyond the delay kernels considered in this paper and \citep{Patra:2015}, the extent of leakage will depend both on the angular structure of the primary beam, which is established in \citep{Neben:2015b} and the model of the foregrounds themselves. In this section, we investigate the amplitude of foreground leakage as a function of delay given an angular primary beam model and two models of the delay structure of the dish: one in which the frequency structure is constant in all directions, and another in which we take into account the increased spectral structure that we observed in \S~\ref{ssec:Sidelobes}.

@@

\subsection{The Impact of Delay-Rate Filtering.}
